Board games group recomendation using metadata

### 2024-12-09 paper v2/paper v2.tex
fix: percentages of training and testing
feat: agregadas tablas de resultados

The final dataset will have 1500 games and 15k users, and will be used for the rest of the project. The dataset will be split into a training and a test set, with 80\% of the data being used for training and 20\% for testing.

@@

>>>>

The final dataset will have 1500 games and 15k users, and will be used for the rest of the project. The dataset will be split into a training and a test set, with 75\% of the data being used for training and 25\% for testing.

@@

\begin{table}[]
    \centering
    \begin{tabular}{|l|l|l|l|}
        \hline
        \textbf{Statistic} & \textbf{LightFM} & \textbf{SVD} & \textbf{Most Popular} \\ \hline
        Precision          & 0.3660           & 0.2020       & 0.3010                \\
        Recall@5           & 0.0942           & 0.0520       & 0.0766                \\
        nDCG@5             & 0.6232           & 0.4762       & 0.5903                \\
        Relevance Score    & 2.76             & 1.59         & 2.32                  \\
        Diversity          & 0.03             & 0.01         & 0.01                  \\
        Novelty            & 5.89             & 8.52         & 5.70                  \\
        Fairness           & 0.60             & 0.72         & 0.66                  \\
        Serendipity        & 4.51             & 2.80         & 3.63                  \\ \hline
    \end{tabular}
    \caption{Random groups recomendation results}
    \label{tab:resultados-modelos}
\end{table}

\begin{table}[]
    \centering
    \begin{tabular}{|l|l|l|l|}
        \hline
        \textbf{Statistic} & \textbf{LightFM} & \textbf{SVD} & \textbf{Most Popular} \\ \hline
        Precision          & 0.3350           & 0.2040       & 0.3240                \\
        Recall@5           & 0.0821           & 0.0498       & 0.0749                \\
        nDCG@5             & 0.5722           & 0.4736       & 0.5474                \\
        Relevance Score    & 2.57             & 1.62         & 2.48                  \\
        Diversity          & 0.04             & 0.01         & 0.01                  \\
        Novelty            & 5.99             & 8.60         & 5.70                  \\
        Fairness           & 0.63             & 0.72         & 0.64                  \\
        Serendipity        & 4.61             & 2.75         & 4.06                  \\ \hline
    \end{tabular}
    \caption{Similar groups recommendation results}
    \label{tab:resultados-modelos-similar}
\end{table}
